### 2020-02-09 paper/introduction.tex
Comments from Reviewer 2 (main) after Andrei's review

Cui \emph{et al.} (2017-2018) used an in-house developed tool to study the thorium fuel cycle transition based on MSBR by employing enriched uranium and Pu as the startup fissile materials. Two scenarios, a Breeding and Burning (B\&B) scenario and a Pre-breeding scenario, were investigated to achieve the fuel cycle transition. Cui \emph{et al.} found that the fuel transition can be achieved by using: (1) enriched uranium with greater than 40\% concentration of $^{235}$U (2) Pu from LWR (burn-up of 60 GWd/t) spent nuclear fuel by applying 60 days of chemical reprocessing \cite{cui2017transition,cui2018possible}.

@@

>>>>

@@

Cui \emph{et al.} (2017-2018) analyzed the fuel transition from enriched $^{235}$U/Th and Pu/Th to $^{233}$U/Th for the MSBR-like design. Cui \emph{et al.} found that the fuel transition can be achieved by using: (1) enriched uranium with greater than 40\% enrichment, which rises the proliferation concerns; (2) Pu from LWR (burn-up of 60 GWd/t) spent nuclear fuel \cite{cui2017transition,cui2018possible}.

The research effort described in \cite{cui2017transition} and
\cite{cui2018possible} is most similar to the work
presented in this paper. However, a few major differences
are: (1) we used built-in truly continuous fuel depletion capabilities in
SERPENT-2 \cite{aufiero2013extended} while Cui \emph{et al.} employed an in-house tool named MSR
Reprocessing Sequence (MSR-RS) \cite{ZOU2015114} which couples with SCALE and employs a batch-wise approach (the burnup simulation stops at a given time and restarts with a new liquid fuel composition after removal of discarded materials and addition of fissile/fertile materials); (2) we investigated different initial loading cases (HALEU, Pu+HALEU, reactor-grade Pu, TRU and $^{233}$U) while Cui \emph{et al.} studied only uranium and Pu as the startup fissile materials; (3) we adopted the SD-TMSR core geometry optimized by Li \emph{et al.} \cite{li_optimization_2018} which is different from the MSBR-like model adopted by Cui \emph{et al.}; (4) Cui \emph{et al.} studied the high-enriched uranium (e$>$90) while we excluded it due to the unavailability of this material for use as an initial reactor fuel (non-proliferation issues) and because the performance of this material is expected to be similar to $^{233}$U; (5) Cui \emph{et al.} introduced two scenarios for thorium fuel cycle transition: a Breeding and Burning (B\&B) scenario and a Pre-breeding scenario while we adopting different approach by introducing two different feed mechanisms: thorium and non-thorium feed mechanism.

In more detail, in current work, the radii of the fuel channels in the outer and inner zone are 5 and 3.5 cm, respectively, while in Cui \emph{et al.} work, all fuel channels have the same radius 2.03 cm, also, the side length of the graphite hexagonal prism is different in both models (7.5 instead of 10 cm in Cui model), total salt volume, density, and composition are different than those used in our study. In Cui's scenarios, the amount of Th is kept constant. $^{233}$U is fed only in (B\&B) scenario and extra fissile materials would have to be added into the core if the produced $^{233}$U is not enough to maintain the reactor criticality. In the Pre-breeding scenario, all the $^{233}$U produced from the decay of the extracted $^{233}$Pa stored outside the core until it reaches the required startup mass for a new reactor. Thus, the criticality of the core is maintained by refueling external fissile material. 
In current work, using the thorium feed mechanism, we simultaneously feed Th and all or part of produced $^{233}$U from the \texttt{Pa-decay tank} into the core. The excess $^{233}$U (if exist) is stored outside the core. In the non-thorium feed mechanism, we continuously inject external heavy metals (HALEU, Pu mixed with HALEU, reactor-grade Pu, or TRU) and part of produced $^{233}$U from the \texttt{Pa-decay tank}. Here we feed a part of produced $^{233}$U because in some cases (e.g., TRU) refueling only external heavy metals failed to maintain the core criticality (limitation is dm$_{total fuel}$ $\leq$ 0.1\%). In the non-thorium feed mechanism, the amount of Th decreases during reactor operation while it is constant in the thorium feed mechanism.
